### 2020-02-24 paper/conclusion.tex
minor changes

We compared the operational and safety parameters of the \gls{SD-TMSR} for the 
three promising startup fuels at both initial and equilibrium states. The total 
temperature coefficient of reactivity is negative and relatively large in all 
cases. For the TRU case, the coefficient remained almost constant during 
operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
evolved from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
60 years of operation. Finally, the six factor evolution during the operation 
was calculated for all three cases, providing a basis for designing the reactivity control system of the \gls{SD-TMSR}.

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
Additionally, the accident safety analysis using coupled 
neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018} will be performed. The full-core SERPENT-2 
model of the \gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in 
this work, will be employed to generate problem-oriented nuclear data 
libraries for Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamic behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios, and 
optimizing the design of various reactor concepts.

>>>>

We compared the operational and safety parameters of the SD-TMSR for the 
three promising startup fuels at both initial and equilibrium states. The total 
temperature coefficient of reactivity is negative and relatively large in all 
cases. For the TRU case, the coefficient remained almost constant during 
operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
evolved from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
60 years of operation.

\section{Future work}
The authors intend to verify obtained results using another tool: batch-wise 
code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
Additionally, the accident safety analysis using coupled 
neutronics/thermal-hydraulics software, Moltres 
\cite{lindsay_introduction_2018} will be performed. The full-core SERPENT-2 
model of the SD-TMSR and equilibrium fuel salt compositions, obtained in 
this work, will be employed to generate problem-oriented nuclear data 
libraries for Moltres. The ultimate goal of this effort is to develop a 
fast-running computational model for studying the dynamic behavior of generic 
\glspl{MSR}, performing safety analysis for different accident scenarios, and 
optimizing the design of various reactor concepts.

### 2020-02-24 paper/introduction.tex
minor changes

Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.

@@

In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study. In Cui's scenarios, the amount of Th is kept constant. $^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality. In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor. Thus, the criticality of the core is maintained by refueling external fissile material. 
In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core. The excess $^{233}$U (if exist) is stored outside the core. In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}. Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%). In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.

>>>>

Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.

@@

Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions. In Cui's scenarios, the amount of Th is kept constant. $^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality. In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor. Thus, the criticality of the core is maintained by refueling external fissile material. 
In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core. The excess $^{233}$U (if exist) is stored outside the core. In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}. Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%). In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.

### 2020-02-24 paper/methods.tex
minor changes

\section{Model description} \label{Model-description}
\subsection{Geometry}
The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design model was introduced by the Chinese Academy of Sciences as a part of  
the strategic project ``Thorium-based Molten-Salt Reactor(TMSR) nuclear energy system" 
\cite{jiang2012advanced,li2015analysis,li_optimization_2018}. The 
design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
\cite{robertson_conceptual_1971} after modifying the geometry to 
control the positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.} 
described the \gls{SD-TMSR} core 
geometry in \cite{li_optimization_2018,ashraf2019whole_core}. 
Figure~\ref{fig:ff} illustrates the quarter-core view of the 
\gls{SD-TMSR}.
The active zone is a right cylinder with height and diameter 
equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
$2.3$ g/cm$^3$, to validate our results against results in literature 
\cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
core. The optimal side length of the graphite hexagonal prism was found in previous work to be 7.5 cm \cite{li_optimization_2018}. The liquid fuel circulates 
continuously through fuel channels that pierce the graphite hexagonal 
prisms. Two radial zones divide the core to enhance 
Th/$^{233}$U breeding performance; the radii of the fuel channels in the 
outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
graphite reflectors surround the core to minimize neutron leakage and 
maximize flux in the core. B${_4}$C cylinder surrounds the reflectors and 
acts as radiation shielding. The \gls{SD-TMSR} pressure vessel is made of a Ni-based (hastelloy N) alloy holds 
the fuel salt, graphite elements, reflector, shielding, and intermediate heat exchanger. The main 
characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

@@

The aim of this paper is to simulate the  
operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

@@

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
SD-TMSR full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of
$1.25\times 10^7$ neutron histories per depletion step. During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant. For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. 
During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.

The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump. We used depletion mode 1 in Serpent-2 (i.e. burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.

>>>>

\section{Model description} \label{Model-description}
\subsection{Geometry}
The SD-TMSR design model was introduced by the Chinese Academy of Sciences as a part of  
the strategic project ``Thorium-based Molten-Salt Reactor(TMSR) nuclear energy system" 
\cite{jiang2012advanced,li2015analysis,li_optimization_2018}. The 
design of the SD-TMSR is inspired by the \gls{MSBR} 
\cite{robertson_conceptual_1971} after modifying the geometry to 
control the positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.} 
described the SD-TMSR core 
geometry in \cite{li_optimization_2018,ashraf2019whole_core}. 
Figure~\ref{fig:ff} illustrates the quarter-core view of the 
SD-TMSR.
The active zone is a right cylinder with height and diameter 
equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
$2.3$ g/cm$^3$, to validate our results against results in literature 
\cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
core. The optimal side length of the graphite hexagonal prism was found in previous work to be 7.5 cm \cite{li_optimization_2018}. The liquid fuel circulates 
continuously through fuel channels that pierce the graphite hexagonal 
prisms. Two radial zones divide the core to enhance 
Th/$^{233}$U breeding performance; the radii of the fuel channels in the 
outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
graphite reflectors surround the core to minimize neutron leakage and 
maximize flux in the core. B${_4}$C cylinder surrounds the reflectors and 
acts as radiation shielding. The SD-TMSR pressure vessel is made of a Ni-based (hastelloy N) alloy holds 
the fuel salt, graphite elements, reflector, shielding, and intermediate heat exchanger. The main 
characteristics of the SD-TMSR are listed in Table~\ref{tab:table1}.

@@

The aim of this paper is to simulate the  
operation of the SD-TMSR for 60 years with various startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assume is unavailable. For that reason, five different types of initial 
fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
Reactor (LWR) spent nuclear fuel (SNF):
\begin{enumerate}[label=(\alph*)]
	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
	\item Pu mixed with \gls{HALEU} (19.79\%),
	\item reactor-grade Pu \cite{marka1993explosive},
	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
\end{enumerate}
All types of initial fissile materials are fed as fluorides.
The reactor-grade Pu and \gls{TRU} compositions are summarized in 
Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

@@

Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
computational software that can support online fuel salt reprocessing and 
refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
SD-TMSR full-core with various initial fuel types. This extension 
of SERPENT accounts for continuous online reprocessing and refueling 
\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
calculations in this work. The results demonstrate full-core runs of
$1.25\times 10^7$ neutron histories per depletion step. During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%). To determine the appropriate depletion step size, we conducted a time step refinement study. We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in K$_{eff}$ became significant. The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
The full burnup time of 
the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
$12$ $pcm$. 
During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere. We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input. Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region. But we did not consider processes, such as decay, which occurs outside of the core. Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.

The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump. We used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material is treated as a single depletion zone.
